Why is it that statistical tests for residuals are not widely used? An explanation using visual inference.

### 2023-01-20 paper_comparison/paper_comparison/paper_comparison.Rmd
e, the constant, is lower case so axis labels adjusted accordingly

```{r}
p <- vi_survey %>%
  filter(x_dist == "uniform") %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  filter(type == "polynomial") %>%
  filter(!null_lineup) %>%
  filter(!attention_check) %>%
  mutate(reject = as.numeric(p_value <= 0.05)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  ggplot() +
  geom_point(data = ~.x %>% 
             group_by(log_effect_size, reject) %>% 
             summarise(num_response = n()),
           aes(log_effect_size, reject, size = factor(num_response)), alpha = 0.3)  +
  geom_smooth(data = mutate(poly_conv_sim, log_effect_size = log(effect_size)) %>%
                select(-(RESET5_p_value:RESET10_p_value)) %>%
                select(-RESET3_p_value, -F_p_value) %>%
                rename(RESET_p_value = RESET4_p_value) %>%
                filter(x_dist == "uniform") %>%
                pivot_longer(RESET_p_value:SW_p_value) %>%
                mutate(name = gsub("_p_value", " test", name)), 
              aes(log_effect_size, as.numeric(value < 0.05), col = name), 
              method = "glm", 
              method.args = list(family = binomial),
              se = FALSE) +
  stat_smooth(geom = "line", 
              data = ~boot_y(.x, reject, times = 500), 
              aes(log_effect_size, reject, group = boot_id, col = "Visual test"), 
              method = "glm", 
              method.args = list(family = binomial), 
              se = FALSE, 
              alpha = 0.03) +
  geom_smooth(aes(log_effect_size, reject, col = "Visual test"), method = "glm", method.args = list(family = binomial), se = FALSE) +
  theme_light(base_size = 5) +
  theme(panel.grid.major.x =  element_line(colour = "grey70", linewidth = 0.5)) +
  scale_color_manual(values = rev(rcartocolor::carto_pal(4, "Vivid"))) +
  scale_size_manual(values = c(1, 2, 3)) +
  scale_x_continuous(breaks = seq(0, 5, 0.5), minor_breaks = NULL) +
  xlab("Effect size (log E)") +
  ylab("Power") +
  labs(col = "", size = "# lineups")
```

@@

```{r}
p <- vi_survey %>%
  filter(x_dist == "uniform") %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  filter(type == "heteroskedasticity") %>%
  filter(!null_lineup) %>%
  filter(!attention_check) %>%
  mutate(reject = as.numeric(p_value <= 0.05)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  ggplot() +
  geom_point(data = ~.x %>% 
               group_by(log_effect_size, reject) %>% 
               summarise(num_response = n()),
             aes(log_effect_size, reject, size = factor(num_response)), alpha = 0.3) +
  geom_smooth(data = mutate(heter_conv_sim, log_effect_size = log(effect_size)) %>%
                filter(x_dist == "uniform") %>%
                select(-(RESET5_p_value:RESET10_p_value)) %>%
                select(-RESET3_p_value, -F_p_value) %>%
                rename(RESET_p_value = RESET4_p_value) %>%
                pivot_longer(RESET_p_value:SW_p_value) %>%
                mutate(name = gsub("_p_value", " test", name)), 
              aes(log_effect_size, as.numeric(value < 0.05), col = name), 
              method = "glm", 
              method.args = list(family = binomial),
              se = FALSE) +
  stat_smooth(geom = "line", 
              data = ~boot_y(.x, reject, times = 500), 
              aes(log_effect_size, reject, group = boot_id, col = "Visual test"), 
              method = "glm", 
              method.args = list(family = binomial), 
              se = FALSE, 
              alpha = 0.03) +
  geom_smooth(aes(log_effect_size, reject, col = "Visual test"), method = "glm", method.args = list(family = binomial), se = FALSE) +
  theme_light(base_size = 5) +
  theme(panel.grid.major.x =  element_line(colour = "grey70", linewidth = 0.5)) +
  scale_color_manual(values = rev(rcartocolor::carto_pal(4, "Vivid"))) +
  scale_x_continuous(breaks = seq(0, 5, 0.5), minor_breaks = NULL) +
  scale_size_manual(values = c(1, 2, 3)) +
  xlab("Effect size (log E)") +
  ylab("Power") +
  labs(col = "", size = "# lineups")
```

@@

```{r}
poly_conv_sim %>%
  filter(x_dist == "uniform", shape %in% c(3, 4)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  select(shape, log_effect_size, (RESET3_p_value:RESET9_p_value)) %>%
  pivot_longer(RESET3_p_value:RESET9_p_value) %>%
  mutate(name = gsub("_p_value", " ", name)) %>%
  mutate(name = gsub("RESET", "", name)) %>%
  mutate(name = gsub("test", "", name)) %>%
  mutate(reject = as.numeric(value < 0.05)) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject, col = name), 
              se = FALSE, 
              method = "glm",
              method.args = list(family = binomial())) +
  xlab("Effect size (log E)") +
  ylab("Power") +
  scale_color_manual(values = rev(rcartocolor::carto_pal(7, "RedOr"))) +
  theme_light() +
  labs(col = "RESET test order") +
  facet_wrap(~shape)
```

```{r}
heter_conv_sim %>%
  filter(x_dist == "uniform") %>%
  mutate(log_effect_size = log(effect_size)) %>%
  mutate(reject = as.numeric(BP_p_value < 0.05)) %>%
  mutate(a = c("left-triangle", "butterfly", "right-triangle")[a + 2]) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject, col = factor(a)), 
              se = FALSE, 
              method = "glm",
              method.args = list(family = binomial())) +
  xlab("Effect size (log E)") +
  ylab("Power") +
  scale_color_manual(values = rcartocolor::carto_pal(3, "Vivid")) +
  theme_light() +
  labs(col = "Heteroskedasticity shape") +
  ggtitle("Conventional test")
```

```{r}
vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(x_dist == "uniform", type == "heteroskedasticity") %>%
  mutate(log_effect_size = log(effect_size)) %>%
  mutate(reject = as.numeric(p_value < 0.05)) %>%
  mutate(a = c("left-triangle", "butterfly", "right-triangle")[a + 2]) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject, col = factor(a)), 
              se = FALSE, 
              method = "glm",
              method.args = list(family = binomial())) +
  xlab("Effect size (log E)") +
  ylab("Power") +
  scale_color_manual(values = rcartocolor::carto_pal(3, "Vivid")) +
  theme_light() +
  labs(col = "Heteroskedasticity shape") +
  ggtitle("Visual test")
```

@@

## Effect of the distribution of the regressor

@@

dat_different_dist %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, 
                  reject, 
                  col = x_dist), 
              method = "glm", 
              method.args = list(family = binomial), 
              se = FALSE) +
  theme_light(base_size = 5) +
  scale_color_manual(values = rcartocolor::carto_pal(4, "Safe")[c(1,3,2,4)]) +
  scale_size_manual(values = c(1, 2, 3)) +
  xlab("Effect size (log E)") +
  ylab("Power") +
  labs(col = "Distribution of regressor", linetype = "Test") +
  facet_wrap(~conv_or_not)
```

>>>>

```{r}
p <- vi_survey %>%
  filter(x_dist == "uniform") %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  filter(type == "polynomial") %>%
  filter(!null_lineup) %>%
  filter(!attention_check) %>%
  mutate(reject = as.numeric(p_value <= 0.05)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  ggplot() +
  geom_point(data = ~.x %>% 
             group_by(log_effect_size, reject) %>% 
             summarise(num_response = n()),
           aes(log_effect_size, reject, size = factor(num_response)), alpha = 0.3)  +
  geom_smooth(data = mutate(poly_conv_sim, log_effect_size = log(effect_size)) %>%
                select(-(RESET5_p_value:RESET10_p_value)) %>%
                select(-RESET3_p_value, -F_p_value) %>%
                rename(RESET_p_value = RESET4_p_value) %>%
                filter(x_dist == "uniform") %>%
                pivot_longer(RESET_p_value:SW_p_value) %>%
                mutate(name = gsub("_p_value", " test", name)), 
              aes(log_effect_size, as.numeric(value < 0.05), col = name), 
              method = "glm", 
              method.args = list(family = binomial),
              se = FALSE) +
  stat_smooth(geom = "line", 
              data = ~boot_y(.x, reject, times = 500), 
              aes(log_effect_size, reject, group = boot_id, col = "Visual test"), 
              method = "glm", 
              method.args = list(family = binomial), 
              se = FALSE, 
              alpha = 0.03) +
  geom_smooth(aes(log_effect_size, reject, col = "Visual test"), method = "glm", method.args = list(family = binomial), se = FALSE) +
  theme_light(base_size = 5) +
  theme(panel.grid.major.x =  element_line(colour = "grey70", linewidth = 0.5)) +
  scale_color_manual(values = rev(rcartocolor::carto_pal(4, "Vivid"))) +
  scale_size_manual(values = c(1, 2, 3)) +
  scale_x_continuous(breaks = seq(0, 5, 0.5), minor_breaks = NULL) +
  xlab("Effect size (log e)") +
  ylab("Power") +
  labs(col = "", size = "# lineups")
```

@@

```{r}
p <- vi_survey %>%
  filter(x_dist == "uniform") %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  filter(type == "heteroskedasticity") %>%
  filter(!null_lineup) %>%
  filter(!attention_check) %>%
  mutate(reject = as.numeric(p_value <= 0.05)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  ggplot() +
  geom_point(data = ~.x %>% 
               group_by(log_effect_size, reject) %>% 
               summarise(num_response = n()),
             aes(log_effect_size, reject, size = factor(num_response)), alpha = 0.3) +
  geom_smooth(data = mutate(heter_conv_sim, log_effect_size = log(effect_size)) %>%
                filter(x_dist == "uniform") %>%
                select(-(RESET5_p_value:RESET10_p_value)) %>%
                select(-RESET3_p_value, -F_p_value) %>%
                rename(RESET_p_value = RESET4_p_value) %>%
                pivot_longer(RESET_p_value:SW_p_value) %>%
                mutate(name = gsub("_p_value", " test", name)), 
              aes(log_effect_size, as.numeric(value < 0.05), col = name), 
              method = "glm", 
              method.args = list(family = binomial),
              se = FALSE) +
  stat_smooth(geom = "line", 
              data = ~boot_y(.x, reject, times = 500), 
              aes(log_effect_size, reject, group = boot_id, col = "Visual test"), 
              method = "glm", 
              method.args = list(family = binomial), 
              se = FALSE, 
              alpha = 0.03) +
  geom_smooth(aes(log_effect_size, reject, col = "Visual test"), method = "glm", method.args = list(family = binomial), se = FALSE) +
  theme_light(base_size = 5) +
  theme(panel.grid.major.x =  element_line(colour = "grey70", linewidth = 0.5)) +
  scale_color_manual(values = rev(rcartocolor::carto_pal(4, "Vivid"))) +
  scale_x_continuous(breaks = seq(0, 5, 0.5), minor_breaks = NULL) +
  scale_size_manual(values = c(1, 2, 3)) +
  xlab("Effect size (log e)") +
  ylab("Power") +
  labs(col = "", size = "# lineups")
```

@@

```{r}
poly_conv_sim %>%
  filter(x_dist == "uniform", shape %in% c(3, 4)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  select(shape, log_effect_size, (RESET3_p_value:RESET9_p_value)) %>%
  pivot_longer(RESET3_p_value:RESET9_p_value) %>%
  mutate(name = gsub("_p_value", " ", name)) %>%
  mutate(name = gsub("RESET", "", name)) %>%
  mutate(name = gsub("test", "", name)) %>%
  mutate(reject = as.numeric(value < 0.05)) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject, col = name), 
              se = FALSE, 
              method = "glm",
              method.args = list(family = binomial())) +
  xlab("Effect size (log e)") +
  ylab("Power") +
  scale_color_manual(values = rev(rcartocolor::carto_pal(7, "RedOr"))) +
  theme_light() +
  labs(col = "RESET test order") +
  facet_wrap(~shape)
```

```{r}
heter_conv_sim %>%
  filter(x_dist == "uniform") %>%
  mutate(log_effect_size = log(effect_size)) %>%
  mutate(reject = as.numeric(BP_p_value < 0.05)) %>%
  mutate(a = c("left-triangle", "butterfly", "right-triangle")[a + 2]) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject, col = factor(a)), 
              se = FALSE, 
              method = "glm",
              method.args = list(family = binomial())) +
  xlab("Effect size (log e)") +
  ylab("Power") +
  scale_color_manual(values = rcartocolor::carto_pal(3, "Vivid")) +
  theme_light() +
  labs(col = "Heteroskedasticity shape") +
  ggtitle("Conventional test")
```

```{r}
vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(x_dist == "uniform", type == "heteroskedasticity") %>%
  mutate(log_effect_size = log(effect_size)) %>%
  mutate(reject = as.numeric(p_value < 0.05)) %>%
  mutate(a = c("left-triangle", "butterfly", "right-triangle")[a + 2]) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject, col = factor(a)), 
              se = FALSE, 
              method = "glm",
              method.args = list(family = binomial())) +
  xlab("Effect size (log e)") +
  ylab("Power") +
  scale_color_manual(values = rcartocolor::carto_pal(3, "Vivid")) +
  theme_light() +
  labs(col = "Heteroskedasticity shape") +
  ggtitle("Visual test")
```

@@

## Effect of the fitted value distribution

@@

dat_different_dist %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, 
                  reject, 
                  col = x_dist), 
              method = "glm", 
              method.args = list(family = binomial), 
              se = FALSE) +
  theme_light(base_size = 5) +
  scale_color_manual(values = rcartocolor::carto_pal(4, "Safe")[c(1,3,2,4)]) +
  scale_size_manual(values = c(1, 2, 3)) +
  xlab("Effect size (log e)") +
  ylab("Power") +
  labs(col = "Distribution of regressor", linetype = "Test") +
  facet_wrap(~conv_or_not)
```

### 2023-01-20 paper_comparison/paper_comparison/paper_comparison.tex
e, the constant, is lower case so axis labels adjusted accordingly

\hypertarget{effect-of-the-distribution-of-the-regressor}{%
\subsection{Effect of the distribution of the
regressor}\label{effect-of-the-distribution-of-the-regressor}}

>>>>

\hypertarget{effect-of-the-fitted-value-distribution}{%
\subsection{Effect of the fitted value
distribution}\label{effect-of-the-fitted-value-distribution}}
